### 2023-02-15 main.tex
Fixed
;

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}=&2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}
	\end{split}
\end{equation}

%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{1k}^{[a]}e_{ki}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
	B_{j}^{2L-1}=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

>>>>

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}
	\end{split}
\end{equation}

%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{1k}^{[a]}e_{ki}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
	\end{split}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form
